Select-based random access to variable-byte encodings

### 2020-03-05 gradu/msc_english_contents.tex
Updated results

\begin{table}
\centering
\caption{Results in milliseconds, smaller is better.\label{table:results1}}
\begin{tabular}{l||c c c c c c c} 
& bris8 & bris4 & bris8v5 & bris4v5 & select8 & select4  \\
 \hline \hline 
all (5M)   & 194.50 & 473.00 & 232.40 & 578.00 & 133.50 & 186.10 \\
all (50M)   & 270.90 & 580.00 & 323.80 & 786.50 & 214.30 & 291.50 \\
all (500M)   & 298.90 & 678.80 & 368.80 & 940.30 & 308.10 & 388.10 \\
twolarge (5M)   & 92.60 & 270.70 & 109.60 & 328.90 & 117.20 & 166.50 \\
twolarge (50M)   & 140.60 & 378.30 & 159.20 & 458.50 & 210.60 & 269.60 \\
twolarge (500M)   & 168.50 & 439.90 & 191.30 & 586.00 & 304.50 & 382.10 \\
onelarge (5M)   & 26.10 & 42.20 & 27.20 & 50.10 & 95.30 & 106.10 \\
onelarge (50M)   & 50.00 & 91.20 & 51.20 & 104.90 & 199.60 & 239.90 \\
onelarge (500M)   & 55.20 & 100.50 & 59.00 & 123.90 & 294.70 & 351.30 \\
onlysmall (5M)   & 16.60 & 21.10 & 16.60 & 23.00 & 80.20 & 95.10 \\
onlysmall (50M)   & 31.60 & 51.90 & 32.40 & 57.00 & 186.50 & 227.30 \\
onlysmall (500M)   & 34.40 & 56.00 & 35.00 & 63.50 & 279.30 & 335.40 \\

>>>>

\begin{table}
\centering
\caption{Results in milliseconds, smaller is better.\label{table:results1}}
\begin{tabular}{l||c c c c c c c} 
& bris8 & bris4 & bris8v5 & bris4v5 & select8 & select4  \\
 \hline \hline 
all (5M)   & 191.80 & 471.50 & 234.00 & 569.40 & 149.20 & 175.90 \\
all (50M)   & 269.20 & 573.80 & 323.00 & 785.00 & 245.40 & 275.00 \\
all (500M)   & 298.50 & 677.80 & 368.20 & 941.80 & 355.90 & 382.20 \\
twolarge (5M)   & 96.70 & 275.50 & 110.70 & 329.00 & 125.60 & 151.90 \\
twolarge (50M)   & 140.40 & 379.70 & 159.80 & 456.80 & 227.70 & 242.20 \\
twolarge (500M)   & 168.20 & 441.00 & 191.50 & 584.70 & 330.20 & 341.00 \\
onelarge (5M)   & 25.80 & 40.10 & 28.30 & 49.20 & 95.90 & 100.40 \\
onelarge (50M)   & 49.80 & 91.30 & 50.90 & 105.70 & 212.70 & 213.20 \\
onelarge (500M)   & 55.00 & 100.00 & 58.50 & 124.00 & 315.80 & 307.70 \\
onlysmall (5M)   & 16.50 & 20.20 & 16.50 & 23.80 & 84.70 & 88.40 \\
onlysmall (50M)   & 31.20 & 51.80 & 32.10 & 57.00 & 201.20 & 198.80 \\
onlysmall (500M)   & 34.10 & 56.00 & 35.00 & 63.10 & 297.90 & 293.80 \\
